---
title: "OpenSAFELY Winter pressures"
author: "OpenSAFELY collaborative"
date: 2023-03-28
# output: powerpoint_presentation
output:
    html_document:
        number_sections: false
        toc: true
---

```{r echo=FALSE, message=FALSE, warning=FALSE }
library(readr)
library(knitr)
library(here)
library(magrittr)
library(stringr)
library(dplyr)
library(glue)
library(R.utils)

knitr::opts_chunk$set( echo=FALSE, message=FALSE, warning=FALSE )

source( here( "reports", "report_variables.R" ) )
source( here( "analysis", "utils.R" ) )

# set output directory
output_directory <- fs::dir_create(
path = here("output", 
            "docs")
)

```

# Winter pressures: introduction

# Metrics of services being overwhelmed

# Variation in service pressure between practices and regions


```{r}
sro_deciles_format = "deciles_chart_.*_practice_only_rate\\.png"
kids_deciles_format = "deciles_chart_.*12_appt.*\\.png"
appt_deciles_format = "deciles_chart_.*\\.png"

sro_decile_plots = list.files(
    path=metrics_directory_shaded,
    pattern=sro_deciles_format,
    full.names = TRUE
)

kids_decile_plots = list.files(
    path=metrics_directory_shaded,
    pattern=kids_deciles_format,
    full.names = TRUE
)

appt_decile_plots = list.files(
    path=appt_directory_shaded,
    pattern=appt_deciles_format,
    full.names = TRUE
)

all_decile_plots = tibble(
    filename = c(
        sro_decile_plots,
        kids_decile_plots,
        appt_decile_plots )
) %>% mutate( name = filename %>%
    basename %>%
    str_remove("^deciles_chart_") %>%
    str_remove(".png$" )
) %>% 
    left_join( measure_descriptions, by=c("name"="long_name"))

```

```{r, results="asis"}

for ( i in 1:nrow(all_decile_plots) ) {
    this_file = all_decile_plots$filename[i]
    this_title = all_decile_plots$description[i]
    print( glue( "### {this_title}\n\n") )
    print( glue( "![{this_title}: decile plot]({this_file})\n\n" ) )
}

```

```{r}

practice_file = here("output","metrics","practices_to_remove.csv")
num_practices_removed = countLines(practice_file)[1]-1

```

Before calculating the seasonal comparisons, we filtered out practices that:

1. had a list size of less than 1000 
2. changed >10% between the start and end of the period

This removed `r num_practices_removed` practices.

## Summary statistics for all seasonal comparisons

Disclosivity controls are as follows:

1. counts below `r formals(redact_and_round)$redact_below` are redacted and replacted with the string "`r formals(redact_and_round)$redaction_string`"
2. counts are then rounded to `r formals(redact_and_round)$round_to` 

```{r, results="asis"}

summary_statistics_file = here("output","combined","seasonal_summaries_nondisclosive.csv")


summary_statistics = read_csv( summary_statistics_file )

focus_method = "seasonal_log2_ratio"

print( glue( "### {method_labels[focus_method]}\n\n") )

print( glue( "This is defined as: {method_formula[focus_method]}\n\n") )

stats_to_print = summary_statistics %>%
    filter( method == focus_method )  %>%
    left_join( measure_descriptions, by=c("variable"="short_name")) %>%
    select( -variable, -method, -long_name ) %>%
    select( description, year, everything() ) %>%
    arrange( year, description )

these_column_names = get_statistics_labels(stats_to_print %>% colnames)

stats_to_print %>%
    kable( col.names=these_column_names ) %>%
    print


```

## Seasonal comparisons


```{r}

target_ratio_file = "summer_winter_ratio_histogram_redacted.png"
target_ratio_metrics = list.files( path=here("output","metrics"), pattern=target_ratio_file, full.names=TRUE, recursive=TRUE )
target_ratio_appts = list.files( path=here("output","appointments"), pattern=target_ratio_file, full.names=TRUE, recursive=TRUE )
all_seasonal_ratio_histogram_filenames = c( target_ratio_metrics, target_ratio_appts )

```

```{r}

all_seasonal_ratios = tibble(
    filename = c( all_seasonal_ratio_histogram_filenames )
) %>% mutate( name = filename %>%
    dirname %>%
    str_remove("/redacted") %>%
    basename
) %>% 
rename( ratio_filename = filename )

all_seasonal_comparisons = all_seasonal_ratios %>% 
    left_join( measure_descriptions, by=c("name"="short_name"))

```

```{r, results="asis"}

for ( i in 1:nrow(all_seasonal_comparisons) ) {
    this_ratio_file = all_seasonal_comparisons$ratio_filename[i]
    this_title = all_seasonal_comparisons$description[i]
    print( glue( "### {this_title}\n\n") )

    print( glue( "![{this_title}: seasonal log2 ratio plot]({this_ratio_file})\n\n" ) )
}

```


# Patient outcomes in outlier practices

```{r}

target_epi_file = ".*_combined.png"
epi_plot_list = list.files( path=here("output","epi","plots","combined"), pattern=target_epi_file, full.names=TRUE )


all_epi_plots = tibble(
    filename = c( epi_plot_list )
    ) %>% mutate ( name = filename %>%
        basename %>%
        str_remove("_combined.png" )
    ) %>% 
    rename( epi_filename = filename ) %>%
    left_join( measure_descriptions, by=c("name"="short_name")) %>%
    arrange( description )

```


```{r, results="asis"}

for ( i in 1:nrow(all_epi_plots) ) {
    this_epi_file = all_epi_plots$epi_filename[i]
    this_title = all_epi_plots$description[i]
    print( glue( "### {this_title}\n\n") )

    print( glue( "![{this_title}: IRR patient outcomes]({this_epi_file})\n\n" ) )
}

```
