---
title: "OpenSAFELY Winter pressures"
author: "OpenSAFELY collaborative"
date: 2023-03-28
# output: powerpoint_presentation
output:
    html_document:
        number_sections: false
        toc: true
---

```{r echo=FALSE, message=FALSE, warning=FALSE }
library(readr)
library(knitr)
library(here)
library(magrittr)
library(stringr)
library(dplyr)
library(glue)

knitr::opts_chunk$set( echo=FALSE, message=FALSE, warning=FALSE )

source( here( "reports", "report_variables.R" ) )
source( here( "analysis", "utils.R" ) )

# set output directory
output_directory <- fs::dir_create(
path = here("output", 
            "docs")
)

```

# Winter pressures: introduction

# Metrics of services being overwhelmed

```{r}
sro_deciles_format = "deciles_chart_.*_practice_only_rate\\.png"
kids_deciles_format = "deciles_chart_.*12_appt.*\\.png"
appt_deciles_format = "deciles_chart_.*\\.png"

sro_decile_plots = list.files(
    path=metrics_directory,
    pattern=sro_deciles_format,
    full.names = TRUE
)

kids_decile_plots = list.files(
    path=metrics_directory,
    pattern=kids_deciles_format,
    full.names = TRUE
)

appt_decile_plots = list.files(
    path=appt_directory,
    pattern=appt_deciles_format,
    full.names = TRUE
)

all_decile_plots = tibble(
    filename = c(
        sro_decile_plots,
        kids_decile_plots,
        appt_decile_plots )
) %>% mutate( name = filename %>%
    basename %>%
    str_remove("^deciles_chart_") %>%
    str_remove(".png$" )
) %>% 
    left_join( measure_descriptions, by=c("name"="long_name"))

```

```{r, results="asis"}

for ( i in 1:nrow(all_decile_plots) ) {
    this_file = all_decile_plots$filename[i]
    this_title = all_decile_plots$description[i]
    print( glue( "### {this_title}\n\n") )
    print( glue( "![{this_title}: decile plot]({this_file})\n\n" ) )
}

```

# Variation in service pressure between practices and regions

## Summary statistics for all seasonal comparisons

Disclosivity controls are as follows:

1. counts below `r formals(redact_and_round)$redact_below` are redacted and replacted with the string "`r formals(redact_and_round)$redaction_string`"
2. counts are then rounded to `r formals(redact_and_round)$round_to` 

```{r, results="asis"}

summary_statistics_file = here("output","combined","seasonal_summaries_nondisclosive.csv")

summary_statistics = read_csv( summary_statistics_file )

method_list = summary_statistics %>% pull( method ) %>% unique

for ( this_method in method_list ) {

    print( glue( "### {method_labels[this_method]}\n\n") )

    print( glue( "This is defined as: {method_formula[this_method]}\n\n") )

    stats_to_print = summary_statistics %>%
        filter( method == this_method )  %>%
        left_join( measure_descriptions, by=c("variable"="short_name")) %>%
        select( -variable, -method, -long_name ) %>%
        select( description, year, everything() ) %>%
        arrange( year )

    these_column_names = get_statistics_labels(stats_to_print %>% colnames)

    stats_to_print %>%
        kable( col.names=these_column_names ) %>%
        print
}

```

## Seasonal comparisons


```{r}

target_ratio_file = "summer_winter_ratio_histogram.png"
all_seasonal_ratio_histogram_filenames = list.files( path=here(), pattern=target_ratio_file, full.names=TRUE, recursive=TRUE )

target_difference_file = "summer_winter_difference_histogram.png"
all_seasonal_difference_histogram_filenames = list.files( path=here(), pattern=target_difference_file, full.names=TRUE, recursive=TRUE )

```

```{r}

all_seasonal_ratios = tibble(
    filename = c( all_seasonal_ratio_histogram_filenames )
) %>% mutate( name = filename %>%
    dirname %>%
    basename
) %>% 
rename( ratio_filename = filename )

all_seasonal_differences = tibble(
    filename = c( all_seasonal_difference_histogram_filenames )
) %>% mutate( name = filename %>%
    dirname %>%
    basename
) %>% 
rename( difference_filename = filename )

all_seasonal_comparisons = all_seasonal_ratios %>% 
    left_join( all_seasonal_differences, by="name" ) %>%
    left_join( measure_descriptions, by=c("name"="short_name"))

```

```{r, results="asis"}

for ( i in 1:nrow(all_seasonal_comparisons) ) {
    this_difference_file = all_seasonal_comparisons$difference_filename[i]
    this_ratio_file = all_seasonal_comparisons$ratio_filename[i]
    this_title = all_seasonal_comparisons$description[i]
    print( glue( "### {this_title}\n\n") )

    print( glue( "![{this_title}: seasonal difference plot]({this_difference_file})\n\n" ) )
    print( glue( "![{this_title}: seasonal log2 ratio plot]({this_ratio_file})\n\n" ) )
}

```
# Patient services in outlier practices

# Early warning systems
